Interpersonal Accuracy of Thoughts, Affect, and Personality Traits

### 2022-06-02 manuscript.Rmd
rapport + clean trait data

# reverse coding
negative_keyed_items <- c('perceiver_trait15', 'perceiver_trait8',
                          'perceiver_trait21', 'perceiver_trait25',
                          'perceiver_trait10', 'perceiver_trait18',
                          'perceiver_trait4', 'perceiver_trait16',
                          'target_trait15', 'target_trait8',
                          'target_trait21', 'target_trait25',
                          'target_trait10', 'target_trait18',
                          'target_trait4', 'target_trait16',
                          'judgment_trait15', 'judgment_trait8',
                          'judgment_trait21', 'judgment_trait25',
                          'judgment_trait10', 'judgment_trait18',
                          'judgment_trait4', 'judgment_trait16')

@@

## Descriptive statistics
```{r, include = FALSE}
# descriptives
vars_desc <-
df %>% 
  select(
    InsecAtt, AnxAtt, AvoAtt, Authenticity, Mask, NTB, Loneliness,
    FNE, beqpos, beqneg, beqstr, erqsup, erqrea, RSE, SAT, POW,
    SIAS, SPS, Open, Consc, Extr, Agree, Neurot, Intell, Trust
  ) %>% 
  names()

@@

```{r, include = FALSE}
# Create, clean and format data for analyses
## Personality

@@

```{r}
# personality
df_personality <- import(here::here("data", "samdata.csv"))

df_personality <-
  df_personality %>% 
  mutate(

    Avgtrait = Avgtrait - 1,
    targSRr = targSR - Avgtrait,

    # Note to self: use a loop for these.
    targSRrC = scale(targSRr, scale = FALSE, center = TRUE),
    AvgtraitC = scale(Avgtrait, scale = FALSE, center = TRUE),
    ptraitC = scale(ptrait, scale = FALSE, center = TRUE)
  )

## null model
null1 <- lmer (ptrait ~ (1|PerUn) + (1|TarUn) + (1|DyUn) + (1|Group), 
               data = df_personality)

sjPlot::tab_model(null1)
```

>>>>

# reverse coding
negative_keyed_items <- c('perceiver_trait15', 'perceiver_trait8',
                          'perceiver_trait21', 'perceiver_trait25',
                          'perceiver_trait10', 'perceiver_trait18',
                          'perceiver_trait4', 'perceiver_trait16',
                          'target_trait15', 'target_trait8',
                          'target_trait21', 'target_trait25',
                          'target_trait10', 'target_trait18',
                          'target_trait4', 'target_trait16',
                          'judgment_trait15', 'judgment_trait8',
                          'judgment_trait21', 'judgment_trait25',
                          'judgment_trait10', 'judgment_trait18',
                          'judgment_trait4', 'judgment_trait16',
                          'rapport12', 'rapport13', 'rapport14',
                          'rapport15')

@@

# composite var for rapport
df <- 
  df %>% 
  mutate(rapport = rowMeans(select(., 
                                   rapport1:rapport11,
                                   rapport12_rc:rapport15_rc),
                            na.rm = TRUE),
         # other composite variables are scaled to 0-100
         rapport = rapport - 1,
         rapport = rapport/7 * 100,
         rapport_c = scale(rapport, scale = FALSE)
         ) %>% 
  relocate(rapport, .before = informant_trait1) %>% 
  relocate(rapport_c, .before = rapport)
```

## Descriptive statistics
```{r, include = FALSE}
# descriptives
vars_desc <-
df %>% 
  select(
    rapport, InsecAtt, AnxAtt, AvoAtt, Authenticity, Mask, NTB, Loneliness,
    FNE, beqpos, beqneg, beqstr, erqsup, erqrea, RSE, SAT, POW,
    SIAS, SPS, Open, Consc, Extr, Agree, Neurot, Intell, Trust
  ) %>% 
  names()

@@

```{r, include = FALSE}
# Create, clean and format data for analyses

## Personality (self- AND informant-reports of targets)
df_personality <-
  df %>% 
  select(perceiver_id:group_id,
         judgment_trait1:target_trait26,
         informant_trait1:informant_trait26,
         InsecAtt:Trust, -ends_with("C"), -ASMtot, -beqtot, -SIAPS)

trait_norms <- # average value for each trait
df_personality %>% 
  select(target_trait1:informant_trait26) %>% 
  map_df(., mean, na.rm = TRUE) %>% 
  pivot_longer(., cols = everything(), 
               names_to = "item",
               names_pattern = "(\\d+)$",
               values_to = "norm") %>% 
  mutate(type = c(rep("self_norm", 26), rep("inf_norm", 26))) %>% 
  pivot_wider(names_from = "type", 
              values_from = "norm") %>% 
  mutate(item = as.numeric(item))

df_personality <- 
df_personality %>% 
  pivot_longer(cols = judgment_trait1:informant_trait26,
               names_to = c("trait", "item"),
               names_sep = "_",
               values_to = "rating") %>% 
  mutate(item = parse_number(item)) %>% # could not write the correct regex :(
  pivot_wider(names_from = "trait",
              values_from = "rating") %>% 
  right_join(., trait_norms, by = "item") %>% 
  mutate(self_dist = target - self_norm,
         inf_dist = informant - inf_norm,
         across(c(InsecAtt:Trust, self_norm:inf_dist), 
                scale, scale = FALSE, center = TRUE)
         )

@@

```{r}
null_trait_self <- lmer(judgment ~ 
                (1|perceiver_id) + 
                (1|target_id) + 
                (1|dyad_id) +
                (1|group_id),
              data = df_personality)
```
